Methods for Large Scale Learning to Rank

### 2014-04-07 report/Chapters/CrossBenchmarkComparison.tex
veel repetitief werk gedaan :(

\section{Collecting Evaluation Results}
With a literature review I will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

\section{Evaluation Results Found in Literature}
\begin{table}[!h]
\scalebox{0.85}{

@@

\label{ltr_methods_used}

>>>>

\section{Collecting Evaluation Results}
\label{sec:collecting_evaluation_results}
With a literature review I will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

\section{Evaluation Results Found in Literature}
Table~\ref{tab:ltr_methods_used} gives an overview of the Learning-to-Rank methods for which evaluation results were found for one of the benchmark datasets listed in section~\ref{sec:collecting_evaluation_results} through the literature review process also described in section~\ref{sec:collecting_evaluation_results}.\\

Some studies with evaluation results found through in literature review were not usable for the meta-analysis because they 1) used a different evaluation methodology than other studies using the same benchmark \cite{Geng2011, Lin2012}, 2) provided results for different tasks (e.g. rank aggregation or transfer ranking) \cite{De2011, De2010, Derhami2013, Pan2011b, De2012, Chen2010, Ah-Pine2008, Wang2009c, De2013, Miao2013, Hoi2008, De2012b, Duh2011b, Argentini2012, Qin2010c, Volkovs2013, Desarkar2011, Pan2013, Lin2011b, Volkovs2012, Dammak2011}, 3) added additional features to a benchmark dataset \cite{Bidoki2009, Ding2010}, 4) did not provide exact data for evaluation results (often only in graph form) (), 5) reported evaluation results in a different metric than the metrics chosen for this meta-analysis (), 6) reported a higher performance on baseline methods than official runs (), or 7) did not report any baseline performance that allowed us to check validity of the results \cite{Chakrabarti2008, Wang2012b, Buffoni2011}.
\begin{table}[!h!p]
\scalebox{0.80}{

@@

\label{tab:ltr_methods_used}
